Cooperative Decision Making for Communities of Autonomous Web Services

### 2013-12-09 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame14 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{The classic problem}
    We have a population $N$ of $n$ agents.    
    \begin{definition} [Coalition]~\\
       A coalition $C$ is a set of agents: $C \in 2^N$.
        \begin{itemize}
            \item $N$ is the set of all agents (or players)
            \item $v:2^N \rightarrow R$ is the \emph{valuation function}. For $C \subseteq N$, $v(C)$ is the value obtained by the coalition $C$
        \end{itemize}
        \label {dfn:Coalition}
    \end{definition}

@@

    \begin{center}
        $N = \{1,2,3\}$ \\
        $v(\{1\}) = 0, v(\{2\}) = 0, v(\{3\}) = 0$ \\
        $v(\{1,2\}) = 90, v(\{1,3\}) = 80, v(\{2,3\}) = 70$ \\
        $v(\{1,2,3\}) = 105$ \\
    \end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Computation Tree Logic of Knowledge (CTLK)}
\begin{definition} [Model of CTLK]\label{Model of CTLK}
A model $ \mathcal{M_K}$ $=(S,I,R_t,\{\approx_i|i\in \mathcal{ A}\}, \mathcal{V})$ that belongs to the set of all models $\mathbb{M}$ is a tuple, where:
\begin {itemize}
\item $ S \subseteq L_1 \times \dots \times L_n $ is the set of
reachable global states for the system.
\item $ I \subseteq S $ is a set of initial global states for the system.
\item $ R_t \subseteq S \times S $ is the transition relation defined by $( s,s') \in R_t $ iff there exists a joint action $( a_1, \dots , a_n) \in ACT $ such that $ \tau (s, a_1, \dots, a_n) = s'$.
\item For each agent $i \in \mathcal{A}$, $ \approx _i  \subseteq S \times S
$ is the epistemic accessibility relation defined by $ s \approx_i
s' $ iff $ l_i(s) = l_i(s') $.
\item $ \mathcal{V} : S \rightarrow 2 ^{\Phi_p} $ is a valuation function where $\Phi_p $ is a set of atomic propositions.
\end {itemize}
\label {dfn: Model of CTLK}
\end{definition}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Syntax of CTLK}
\begin{definition} [Syntax of CTLK]\label{Syntax of CTLK}~\\
$~~~~~~~~~~~~~ \varphi ::= p \mid \neg \varphi \mid \varphi \vee
\varphi \mid EX \varphi  \mid E ( \varphi U \varphi) \mid EG
\varphi \mid K_i \varphi$\\
Where:
\begin{itemize}
\item $ p \in \Phi_p$ is an atomic proposition; \item The boolean
connectives $\neg$, and $\vee$ are defined in the usual way; \item
$E$ is the existential quantifier on paths; \item $X$, $U$, and
$G$ are CTL path modal connectives standing for ``next", ``until",
and ``globally" respectively; and \item The modal connective $K_i$
stands for ``knowledge for agent $i$".
\end{itemize}
\label {dfn: Syntax of CTLK}
\end{definition}
In this logic, \textbf{$K_i \varphi$ is read as ``agent $i$ knows
$\varphi"$.}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Satisfaction of CTLK}
\begin{definition} [Satisfaction of CTLK]~\\
Given the model $ \mathcal M$, the satisfaction of a CTLK formula
$ \varphi$ in a global state $ s$, denoted by $ (\mathcal M, s )
\models \varphi$, is recursively defined as follows:

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame14 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{The Classic Problem}
    We have a population $N$ of $n$ agents.
    \begin{definition} [Coalition]~\\
       A coalition $C$ is a set of agents: $C \in 2^N$.
        \begin{itemize}
            \item $N$ is the set of all agents (or players)
            \item $v:2^N \rightarrow R$ is the \emph{valuation function}. For $C \subseteq N$, $v(C)$ is the value obtained by the coalition $C$
        \end{itemize}
        \label {dfn:Coalition}
    \end{definition}

@@

    \begin{center}
        $N = \{1,2,3\}$ \\
        $v(\{1\}) = 0, v(\{2\}) = 0, v(\{3\}) = 0$ \\
        $v(\{1,2\}) = 90$ \\ 
        $v(\{1,3\}) = 80$ \\ 
        $v(\{2,3\}) = 70$ \\
        $v(\{1,2,3\}) = 105$ \\
    \end{center}

    What should we do?
    \begin{itemize}
        \item form $\{1,2,3\}$ and share equally $(35,35,35)$?
        \item 3 can say to 1 ``let's form $\{1,3\}$ and share (40,0,40)''
        \item 2 can say to 1 ``let's form $\{1,2\}$ and share (45,45,0)''
        \item 3 can say to 2 ``OK, let's form $\{2,3\}$ and share (0,46,24)''
        \item 1 can say to 2 and 3, ``fine! $\{1,2,3\}$ and (33,47,25)''
        \item ...what is a good solution?
    \end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Transferable and Non Transferable Utility Games}
    \begin{itemize}
        \item \textbf{Games with Transferable Utility (TU games)}
        \begin{itemize}
            \item Utility is worth the same for all agents
            \item Utility can be {\color{red} compared} or {\color{red} transfered} between agents.
            \item Irrespective of the division of the coalitional payoff, members of the coalition enjoy the same total utility.
        \end{itemize}

        \begin{definition} [Valuation or Characteristic function]\label{dfn:valuationfunction}
            A \emph{valuation function v} associates a real number $v(C)$ to any subset $C \subseteq N$, i.e., $v:2^N \rightarrow R$ \\
            A {\color{blue}\emph{TU game}} is a pair $(N,v)$ where $N$ is a set of agents and where $v$ is a valuation function.
            \label {dfn:valuationfunction}
        \end{definition}

        \item \textbf{Games with Non Transferable Utility (NTU games)} \\
            Agents have different preferences over coalitions and rewards. Non-monetary rewards, i.e. item allocation type of problems where items have different values for different players.
    \end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Syntax of CTLK}
\begin{definition} [Syntax of CTLK]\label{Syntax of CTLK}~\\
$~~~~~~~~~~~~~ \varphi ::= p \mid \neg \varphi \mid \varphi \vee
\varphi \mid EX \varphi  \mid E ( \varphi U \varphi) \mid EG
\varphi \mid K_i \varphi$\\
Where:
\begin{itemize}
\item $ p \in \Phi_p$ is an atomic proposition; \item The boolean
connectives $\neg$, and $\vee$ are defined in the usual way; \item
$E$ is the existential quantifier on paths; \item $X$, $U$, and
$G$ are CTL path modal connectives standing for ``next", ``until",
and ``globally" respectively; and \item The modal connective $K_i$
stands for ``knowledge for agent $i$".
\end{itemize}
\label {dfn: Syntax of CTLK}
\end{definition}
In this logic, \textbf{$K_i \varphi$ is read as ``agent $i$ knows
$\varphi"$.}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Satisfaction of CTLK}
\begin{definition} [Satisfaction of CTLK]~\\
Given the model $ \mathcal M$, the satisfaction of a CTLK formula
$ \varphi$ in a global state $ s$, denoted by $ (\mathcal M, s )
\models \varphi$, is recursively defined as follows:
